### 2019-02-27 paper/ms.tex
Put interloper problem into equation form
Start considering triple and setting up three field approach

>>>>

Assuming perfect foreground removal, if one makes a naive power spectrum
estimate of the observed intensity at a frequency $\mynu{l}{o}$, then the
observed power spectrum will be,
\beq\label{eq:observed_with_int}
P_{\mynu{l}{o}} = P_{l} + \sum_{i} P_{i}\text{.}
\eeq
Since $P_l$ is the object of interest, we must robustly measure and subtract
each of $P_i$.

Now consider an arbitrary triple of the interloping lines $(i, j, k)$ where
none of $i$, $j$, or $k$ are equal (and in particular none of $z_i$, $z_j$, or
$z_k$ are equal). Now consider the case of removing emission from line $i$,
which is interloping at redshift $z_i$. One can cross-correlate line $i$ with
line $j$ if the frequency at which line $j$ is emitted at redshift $z_i$ is
within the observed frequency band. That is, we'd like to observe line $j$ at
a different frequency $\mynu{j}{o}'$ such that the emitted redshift $z_j'$ is
equal to $z_i$, so that we can cross-correlate the two. In other words, we
need $\mynu{j}{o}'$ to satisfy,
\beq\label{eq:nu_obs}
\begin{split}
\mynu{j}{o}' &= \mynu{i}{o} \frac{\mynu{j}{e}}{\mynu{i}{e}} \\
&= \mynu{i}{o} \frac{1+z_j}{1+z_i}\text{.}
\end{split}
\eeq
If the frequency $\mynu{j}{o}'$ is in the observing band of an instrument
(though in a different bin than $\mynu{i}{o}$), then a cross-corelation
between line $i$ and line $j$ can be made. This can be used to measure the
product $B_iB_j$. However, this does not allow us to remove either line $i$ or
line $j$ reliably, since the relevant quantity to subtract from
Equation~\ref{eq:observed_with_int} is $B_i^2 + B_j^2$, for which a direct
constraint cannot be made. Perhaps measurements of the cross-bispectrum may be
possible and allow us to measure $B_i$ and $B_j$ independently
\citep{2018ApJ...867...26B}, but measuring cross-bispectra is difficult in
practice and a reliable cross-spectrum measurement will probably be possible
with less survey area.

However, in the case that $\mynu{k}{o}'$ (defined similarly to
Equation~\ref{eq:nu_obs}) also lies in the observing band, then a three-field
approach can be employed to directly measure each of $B_i^2$, $B_j^2$, and
$B_k^2$.
